---
title: "Third Asset"
---

```{r}
library(xml2)
library(rvest)
library(tibble)
library(purrr)
library(stringr)
library(dplyr)
library(lubridate)
```

### Functions
```{r}
##### intreview_date function ##### 
intreview_date <- function(html){
  html %>%
  html_nodes(".empReview.cf") %>%
  map_df(~list(date = html_nodes(.x,'.date.subtle.small') %>% html_text() %>% {if(length(.) == 0) NA else .})) %>%
  unlist(use.names = FALSE)
}

##### review_title function ##### 
review_title <- function(html){
  html %>%
  html_nodes(".tbl.fill.reviewHdr") %>%
  map_df(~list(title = html_nodes(.x,'.reviewer') %>% html_text() %>% {if(length(.) == 0) NA else .}))
}

##### intreview_location function ##### 
intreview_location <- function(html){
  html %>%
  html_nodes('.tbl.fill.reviewHdr') %>%
  map_df(~list(location = html_node(.x, '.authorLocation') %>% html_text() %>% {if(length(.) == 0) NA else .}))
}

##### intreview_outcome function ##### 
intreview_outcome <- function(html){
  html %>%
  html_nodes(".interviewOutcomes") %>%
  html_text()
}

##### interview_question function ##### 
interview_question <- function(html){
  html %>%
  html_nodes('.tbl.fill.margTopMd') %>%
  map_df(~list(question = html_node(.x, '.interviewQuestions') %>% html_text() %>% {if(length(.) == 0) NA else .}))
}
```

### Inputs
```{r}
url <- "https://www.glassdoor.com/Interview/Amazon-Interview-Questions-E6036_P%d.htm"
last_page <- 1000
pages_url <- str_c(sprintf(url,1:last_page))
pages_url <- gsub("_P1.htm",".htm",pages_url)
pages_url[1]
pages_url[last_page]
```

### Analysis
```{r}
map_df(1:last_page,function(i){
  cat(".")
  page_html <- read_html (pages_url[i])
  Dates <- intreview_date (page_html)
  Title <- review_title (page_html)
  Location <- intreview_location (page_html)
  Outcome <- intreview_outcome (page_html)
    Offer_outcome <- str_extract (Outcome,"Accepted|No")
    Experience_outcome <- str_extract (Outcome,"Positive|Negative")
    Interview_outcome <- str_extract (Outcome,"Difficult|Easy|Average")
  Question <- interview_question (page_html)
  data.frame(Dates,Title,Location,Offer_outcome,Experience_outcome,Interview_outcome,Question,stringsAsFactors = FALSE)
}) -> result
```

### Number of Accepted/Rejected interview in the top 10 job openings in Amazon in a specific office (e.g., Seattle, WA)
```{r}
office_name <- "Seattle, WA"
result_filter <- result %>% filter(location == office_name)
y <- table(result_filter$title, result_filter$Offer_outcome)
y <- tail(y[order(rowSums(y)),],n=10)
y <- t(y)
par(mar=c(14,4,1,0.1))
barplot(y, col = 3:2, legend = c("Accepted","Rejected"), args.legend = list(x ='top'), ylab = "Counts", cex.axis=1.0, cex.name=0.9, las=2, lwd=2, beside=TRUE)
```

### Number of Accepted/Rejected interview in the top 10 job openings in Amazon in a specific office (e.g., Seattle, WA) in a specific year (e.g., 2019)
```{r}
year <- "2019"
office_name <- "Seattle, WA"
result$Dates <- as.Date(result$Dates," %B %d, %Y")
result_filter_1 <- result %>% filter(location == office_name)
result_filter_2 <- result_filter_1 %>% filter(as.numeric(format(Dates,'%Y')) == year)
y <- table(result_filter_2$title, result_filter_2$Offer_outcome)
y <- tail(y[order(rowSums(y)),],n=10)
y <- t(y)
par(mar=c(12,4,1,0.1))
barplot(y, col = 3:2, legend = c("Accepted","Rejected"), args.legend = list(x ='top'), ylab = "Counts", cex.axis=0.8, cex.name=0.8, las=2, lwd=2, beside=TRUE)
```

### Number of Accepted/Rejected interview in the top 10 job openings in Amazon in a specific office (e.g., Seattle, WA) for a specific title (e.g., Software Development Engineer)
```{r}
position <- "Software Development Engineer"
office_name <- "Seattle, WA"
result$Dates <- as.Date(result$Dates," %B %d, %Y")
result_filter_1 <- result %>% filter(location == office_name)
result_filter_2 <- result_filter_1 %>% filter(title == position)
y <- table(as.numeric(format(result_filter_2$Dates,'%Y')), result_filter_2$Offer_outcome)
y <- t(y)
par(mar=c(6,4,1,0.1))
barplot(y, col = 3:2, legend = c("Accepted","Rejected"), args.legend = list(x ='topright'), ylab = "Counts", cex.axis=0.8, cex.name=0.8, las=2, lwd=2, beside=TRUE)
```

### Number of Accepted/Rejected interview in the top 10 job openings in Amazon in a specific office (e.g., Seattle, WA) for a specific title (e.g., Software Development Engineer) in a specific year (e.g. 2017)
```{r}
year <- "2017"
position <- "Software Development Engineer"
office_name <- "Seattle, WA"
result$Dates <- as.Date(result$Dates," %B %d, %Y")
result_filter_1 <- result %>% filter(location == office_name)
result_filter_2 <- result_filter_1 %>% filter(title == position)
result_filter_3 <- result_filter_2 %>% filter(as.numeric(format(Dates,'%Y')) == year)
y <- table(as.numeric(format(result_filter_3$Dates,'%m')), result_filter_3$Offer_outcome)
y <- t(y)
par(mar=c(6,4,1,0.1))
barplot(y, col = 3:2, legend = c("Accepted","Rejected"), args.legend = list(x ='top'), ylab = "Counts", cex.axis=0.8, cex.name=0.8, las=2, lwd=2, beside=TRUE)
```

### Interview questions in the top 10 job openings in Amazon in a specific office (e.g., Seattle, WA) for a specific title (e.g., Software Development Engineer) in a specific year and month (e.g. March, 2017)
```{r}
year <- "2017"
month <- "3"
position <- "Software Development Engineer"
office_name <- "Seattle, WA"
result$Dates <- as.Date(result$Dates," %B %d, %Y")
result_filter_1 <- result %>% filter(location == office_name)
result_filter_2 <- result_filter_1 %>% filter(title == position)
result_filter_3 <- result_filter_2 %>% filter(as.numeric(format(Dates,'%Y')) == year)
result_filter_4 <- result_filter_3 %>% filter(as.numeric(format(Dates,'%m')) == month)
y <- data.frame(result_filter_4$Dates, result_filter_4$question)
y 
```
